Re-finding to support a Deep Web Question Answering System

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
More More New stuff from jnw

We cannot rely on the DBpedia categories and the associated Wikipedia
pages to provide corpora for all our realms.  The categories in
DBpedia store and documents in the Wikipedia are insufficient to
characterize the linguistic space of queries belonging to many
different realms.  Reasonable prior probabilities for the names of
musical groups within the category \emph{musical groups}, for example,
will be significantly different from what would be manufactured by
simply finding n-gram frequency within the related Wikipedia
documents. We are investigating methods to identify categories within
the deep web and to find new sources to construct \textit{weak} realms
in our ontology hierarchy.

>>>>

We cannot rely on the DBpedia categories and the associated Wikipedia
pages to provide corpora for all our realms.  The DBpedia categories
and the associated Wikipedia documents are insufficient to
characterize the linguistic space of queries belonging to many
different realms.  Reasonable prior probabilities for the names of
musical groups within the category \emph{musical groups}, for example,
will be significantly different from what would be manufactured by
simply finding n-gram frequency within the related Wikipedia
documents. We are investigating methods to identify categories within
the deep web and to find new sources to construct \textit{weak} realms
in our ontology hierarchy.
